---
title: "游늵 Mail Data Ad Metrics"
author: "Mark Faynboym"
date: "2025-10-11"
output: 
  html_document:
    toc: true
    theme: yeti
    highlight: pygments
    toc_float: true
    df_print: paged
    number_sections: no  
#     title: "游늵 Mail Data Ad Metrics"
# author: "Mark Faynboym"
# date: "2025-10-11"
# output: 
#   pdf_document:
#     toc: true
#     number_sections: false
# always_allow_html: true
---
# Introduction

We scrape the following OnDemandLending Mail Data from Lodasoft... 

- CRM 
- LOS 
- Loans funded
- Total Mail Count (manually entered)


## 游꿢 Objective: Ad Metrics

We are investigating the effectiveness of our ad campaigns from OndemandLending's marketing contractors (e.g., **Amsive**, **Camber**).  

The goal is to understand how well our ad spend is performing by evaluating the following metrics:

- 游 **Response Rate: **What is the percentage of calls we get by ad company?
- 游 **Call to Lock Rate: ** How many calls turn into locks
- 游눯  **Lock to Fund Rate: ** How many locks convert to a funded loan

We then do <u>further investigation</u>. We look at 

- *Total-Mail-To-Fund: * to look at direct imact of Total mail on funding loans
- *Further exploration: * to see if we can do insights on campaign data that has been given time to reach its clients and it's efficiency on loan-funding. 

We end with a Conclusion, further questions, considerations and fix-me's to improve upon our current analysis.

Feel free to toggle on the table-of-contents to move from one section to another.




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(lubridate)
library(plotly)
library(knitr)
library(kableExtra)
library(DT)
library(patchwork)
```



```{r}
# Load MailData.csv from 'data/processed' folder
maildata <- read_csv("../../data/processed/MailData.csv")
```

```{r}
## Clean code and convert from strings to date and numeric format

# Clean column names from spaces and symbols(ASCII)
maildata <- janitor::clean_names(maildata)

# Convert date column
maildata <- maildata %>%
  mutate(mail_date = mdy(mail_date))

# Convert percentage columns to numeric
percent_cols <- c("response_rate", "call_to_lock", "lock_to_fund")
maildata <- maildata %>%
  mutate(across(all_of(percent_cols), ~ as.numeric(str_remove(., "%"))))

# Convert numeric columns
numeric_cols <- c("calls", "locks", "fundings")
maildata <- maildata %>%
  mutate(across(all_of(numeric_cols), ~ as.numeric(.)))

# Create Mail Multiplier column
maildata <- maildata %>%
  mutate(mail_multiplier = round(10000 / total_mail_pieces, 2))

# Apply multiplier to selected columns
scaled_cols <- c("calls", "locks", "fundings")

maildata <- maildata %>%
  mutate(across(all_of(scaled_cols),
                ~ round(. * mail_multiplier),
                .names = "{.col}_per_10k"))
```

First we generate a table to easily look through and compare values. 

From the start of the year, we have campaigns going back as far as 03/28/2024 so our mail data is generated from 03/28/2024 to capture all of the calls possible for each campaign.


**Please note** that there are some campaigns with NO TOTAL MAIL PIECE VALUES. A separate table is at the bottom of the report of all instances. Please make sure to update. For now we will ignore missing values

# Mail Data Table


```{r}

# Render searchable table with column filters
datatable(
  maildata,
  filter = "top",  # 游녣 adds search boxes at the top of each column
  options = list(
    pageLength = 5,
    scrollX = TRUE
  ),
  rownames = FALSE,
  caption = "游늶 Amsive Campaign Table with Column Filters"
)
```

Now, lets look at the metrics; the response rate, call-to-lock rate and the lock-to-fund rate. 

```{r}
# Prepare data
plot_data <- maildata  %>%   arrange(mail_date) %>% 
  mutate(campaign_name = factor(campaign_name, levels = c("Camber", "Monster", "Amsive", "Redstone")))

#%>%
  # filter(!is.na(campaign_name), !is.na(response_rate)) %>%
  #mutate(response_rate = as.numeric(response_rate))
```

# Response Rate

### Bar graph

We first look at the entire timeline to view data exhaustively. And notice we should only be looking at data, mainly for Camber and Amsive from the start of 2025


```{r}

# Build bar plot with uniform widths and ordered campaigns
p <- ggplot(plot_data, aes(x = mail_date, y = response_rate, fill = campaign_name)) +
  geom_col(position = position_dodge(width = 0.01), width = 7, color = "gray20", alpha = 0.85) +
scale_fill_manual(values = c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA" ,
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)) +
  labs(
    title = "游늵 Response Rate Over Time by Campaign",
    x = "Mail Date",
    y = "Response Rate (%)",
    fill = "Campaign"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Make it interactive
ggplotly(p)
```


So we do just that. 
Two observations made here
1) Camber outperforms Amsive significantly in each campaign.

2) Each campaign has a decreasing trend. This makes sense because campaigns that have been out longer have more time to reach slow-responding clients.

```{r}
# 游릴 Ensure mail_date is a proper Date
plot_data_YTD <- plot_data %>% 
  filter(mail_date >= as.Date("2024-12-30") ) 


p <- ggplot(plot_data_YTD, aes(x = mail_date, y = response_rate, fill = campaign_name)) +
  geom_col(position = position_dodge(width = 0.01), width = 6, color = "gray20", alpha = 0.85) +
scale_fill_manual(values = c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA" ,
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)) +
  labs(
    title = "游늵 Response rate by Campaign (From 04/30/2025)",
    x = "Mail Date",
    y = "FResponse Rate (%) (%)",
    fill = "Campaign"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplotly(p)
```


To have a better visual we make a box plot to look at our values. We only use the dates after 04/30/2025 where both campaigns have roughly the same start times.

Observations: 
Camber is significantly outperforming Amsive

### Box Plot

```{r}
plot_data_datecutoff <- plot_data_YTD %>% filter(mail_date >= as.Date("2025-05-05"))


# 游릴 Build ggplot BoxPlot
p <- ggplot(plot_data_datecutoff %>% filter(!is.na(total_mail_pieces)), aes(x = campaign_name, y = response_rate, fill = campaign_name)) +
  scale_fill_manual(values = c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA" ,
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)) +
  geom_boxplot(alpha = 0.7, color = "gray20") +
  labs(title = "游늳 Response Rate by Campaign",
       x = "Campaign Name",
       y = "Response Rate (%)",
       fill = "Campaign") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")

# Make it interactive
ggplotly(p)
```

### Test of campaigns being equal ( favor is in Camber)

With observations of about 60 total (30 each) a Welch's t-test is appropriate as unequal variance is a possibilty. (Unlike Gosset's Student's t-test which assumes equal variance)


```{r}
# Step 2: Split into groups
amsive_calls <- plot_data$calls_per_10k[plot_data$campaign_name == "Amsive"]
camber_calls <- plot_data$calls_per_10k[plot_data$campaign_name == "Camber"]

# Step 3: Run two-sample t-test
t.test(amsive_calls, camber_calls,
       alternative = "two.sided",
       var.equal = FALSE)  # Welch's t-test (default)

# Step 3: Run one sided test t-test
t.test(camber_calls,amsive_calls, 
       alternative = "greater",
       var.equal = FALSE)  # Welch's t-test (default)
```


# Call-To-Lock

We will continue using the date cut-off of 04/30/2025

### Bar Graph

By looking at the bar graph, we can not draw any conclusive evidence. Let's try a box plot

```{r}
p <- ggplot(plot_data_datecutoff, aes(x = mail_date, y = call_to_lock, fill = campaign_name)) +
  geom_col(position = position_dodge(width = 4), width = 2.6, color = "gray20", alpha = 0.85) +
scale_fill_manual(values = c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA" ,
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)) +
  labs(
    title = "游늵 Call-To_lock by Campaign (From 04/30/2025)",
    x = "Mail Date",
    y = "Calls-To-Lock (%)",
    fill = "Campaign"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplotly(p)
```

### Box Plot

With our box plot we see an interesting change-up. Amsive seems to be outperforming in the call-to-lock portion of our loan pipeline with the median in Amsive being above the 75th percentile in Camber. 

```{r}
# 游릴 Build ggplot BoxPlot
p <- ggplot(plot_data_datecutoff %>% filter(!is.na(calls)), aes(x = campaign_name, y = call_to_lock, fill = campaign_name)) +
  scale_fill_manual(values = c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA" ,
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)) +
  geom_boxplot(alpha = 0.7, color = "gray20") +
  labs(title = "游늳 Call-To-Lock by Campaign (From 04/30/2025)",
       x = "Campaign Name",
       y = "Calls-To-Lock (%)",
       fill = "Campaign") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")

# Make it interactive
ggplotly(p)
```

The tests show that it isn't an anomaly for Amsive to be greater than Camber but still p-value is showing there is something to consider.

```{r}
# Step 2: Split into groups
amsive_calltolock <- plot_data_datecutoff$call_to_lock[plot_data$campaign_name == "Amsive"]
camber_calltolock <- plot_data_datecutoff$call_to_lock[plot_data$campaign_name == "Camber"]

# Step 3: Run two-sample t-test
t.test(amsive_calltolock, camber_calltolock,
       alternative = "two.sided",
       var.equal = FALSE)  # Welch's t-test (default)

# Step 3: Run one sided test t-test
t.test(camber_calltolock,amsive_calltolock, 
       alternative = "greater",
       var.equal = FALSE)  # Welch's t-test (default)
```



# Lock-To-Fund

Now we view the final metric, Lock-To-Fund

### Bar Graph

```{r}
p <- ggplot(plot_data_datecutoff, aes(x = mail_date, y = lock_to_fund, fill = campaign_name)) +
  geom_col(position = position_dodge(width = 4), width = 2.6, color = "gray20", alpha = 0.85) +
scale_fill_manual(values = c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA" ,
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)) +
  labs(
    title = "游늵 Lock-To-Fund by Campaign (From 04/30/2025)",
    x = "Mail Date",
    y = "Lock-To-Fund (%)",
    fill = "Campaign"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplotly(p)
```

### Box plot

Similar to our Call-To-Lock we see that Amsive has some better performance in the Lock-To-Fund portion of the loan pipeline. We should consider that these results may change as more data is gathered in time. 

```{r}
# 游릴 Build ggplot BoxPlot
p <- ggplot(plot_data_datecutoff %>% filter(!is.na(calls)), aes(x = campaign_name, y = lock_to_fund, fill = campaign_name)) +
  scale_fill_manual(values = c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA" ,
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)) +
  geom_boxplot(alpha = 0.7, color = "gray20") +
  labs(title = "游늳 Lock-To-Fund by Campaign (From 04/30/2025)",
       x = "Campaign Name",
       y = "Lock-To-Fund (%)",
       fill = "Campaign") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")

# Make it interactive
ggplotly(p)
```

No test will be drawn as this looks to be less significant than the Call-To-Lock observations, rendering a test useless.


# Summary

```{r}
# Load libraries
library(ggplot2)
library(plotly)
library(dplyr)

# Define color palette
campaign_colors <- c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA",
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)

# Base theme for smaller text
base_theme <- theme_minimal(base_size = 10)

# Create interactive bar charts
bar_response <- ggplotly(
  ggplot(plot_data_datecutoff, aes(x = mail_date, y = response_rate, fill = campaign_name)) +
    geom_col(position = position_dodge(width = 0.01), width = 4, color = "gray20", alpha = 0.85) +
    scale_fill_manual(values = campaign_colors) +
    labs(title = "Response Rate by Mail Date", x = "Mail Date", y = "Response Rate (%)", fill = "Campaign") +
    base_theme +
    theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1))
)

bar_call_to_lock <- ggplotly(
  ggplot(plot_data_datecutoff, aes(x = mail_date, y = call_to_lock, fill = campaign_name)) +
    geom_col(position = position_dodge(width = 0.01), width = 4, color = "gray20", alpha = 0.85) +
    scale_fill_manual(values = campaign_colors) +
    labs(title = "Call-to-Lock by Mail Date", x = "Mail Date", y = "Call-to-Lock (%)", fill = "Campaign") +
    base_theme +
    theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1))
)

bar_lock_to_fund <- ggplotly(
  ggplot(plot_data_datecutoff, aes(x = mail_date, y = lock_to_fund, fill = campaign_name)) +
    geom_col(position = position_dodge(width = 0.01), width = 4, color = "gray20", alpha = 0.85) +
    scale_fill_manual(values = campaign_colors) +
    labs(title = "Response rate                Call-To_lock              Lock-To-Fund by Campaign", x = "Mail Date", y = "Lock-to-Fund (%)", fill = "Campaign") +
    base_theme +
    theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1))
)

# Create interactive box plots
box_response <- ggplotly(
  ggplot(plot_data_datecutoff, aes(x = campaign_name, y = response_rate, fill = campaign_name)) +
    geom_boxplot(alpha = 0.7, color = "gray20") +
    scale_fill_manual(values = campaign_colors) +
    labs(title = "Response Rate by Campaign", x = "Campaign", y = "Response Rate (%)") +
    base_theme +
    theme(legend.position = "none", axis.text.x = element_text(size = 8))
)

box_call_to_lock <- ggplotly(
  ggplot(plot_data_datecutoff, aes(x = campaign_name, y = call_to_lock, fill = campaign_name)) +
    geom_boxplot(alpha = 0.7, color = "gray20") +
    scale_fill_manual(values = campaign_colors) +
    labs(title = "Call-to-Lock by Campaign", x = "Campaign", y = "Call-to-Lock (%)") +
    base_theme +
    theme(legend.position = "none", axis.text.x = element_text(size = 8))
)

box_lock_to_fund <- ggplotly(
  ggplot(plot_data_datecutoff, aes(x = campaign_name, y = lock_to_fund, fill = campaign_name)) +
    geom_boxplot(alpha = 0.7, color = "gray20") +
    scale_fill_manual(values = campaign_colors) +
    labs(title = "Response rate                Call-To_lock              Lock-To-Fund by Campaign", x = "Campaign", y = "Lock-to-Fund (%)") +
    base_theme +
    theme(legend.position = "none", axis.text.x = element_text(size = 8))
)
```

```{r}
#subplot(list(bar_response, bar_call_to_lock, bar_lock_to_fund))
```

When comparing each step in the pipeline it becomes not so clear which ad agency is better. 

```{r}
subplot(list(box_response, box_call_to_lock, box_lock_to_fund))
```

# Total Mail to Fund 

Seeing as how Camber and Amsive each have a portion of the pipeline that they perform better at than their competitor, we will attempt to view the crux of our problem, seeing how much cost (in our case, total mail advertising) we need to input for loans to fund.

We calculate the total fund by 10,000 total mail to make valid comparisons. Observations show Camber may be performing better than Amsive when looking at campaigns that have been given some time to have maximum exposure to the market. We'll continue to explore.

```{r}
p <- ggplot(plot_data_datecutoff, aes(x = mail_date, y = fundings_per_10k, fill = campaign_name)) +
  geom_col(position = position_dodge(width = 4), width = 2.6, color = "gray20", alpha = 0.85) +
scale_fill_manual(values = c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA" ,
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)) +
  labs(
    title = "游늵 Total Mail-To-Fund per 10K total mail by Campaign (From 04/30/2025)",
    x = "Mail Date",
    y = "Total Mail-To-Fund (%)",
    fill = "Campaign"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplotly(p)
```

```{r}
# 游릴 Build ggplot BoxPlot
p <- ggplot(plot_data_datecutoff %>% filter(!is.na(calls)), aes(x = campaign_name, y = fundings_per_10k, fill = campaign_name)) +
  scale_fill_manual(values = c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA" ,
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)) +
  geom_boxplot(alpha = 0.7, color = "gray20") +
  labs(title = "游늵 Total Mail-To-Fund by Campaign (From 04/30/2025)",
    x = "Mail Date",
    y = "Total Mail-To-Fund (%)",,
       fill = "Campaign") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")

# Make it interactive
ggplotly(p)
```


# Additional Exploration

```{r}

# Aggregate by month
monthly_data <- plot_data_datecutoff %>%
  mutate(month = floor_date(mail_date, "month")) %>%
  group_by(month, campaign_name) %>%
  summarise(
    fundings_per_10k = mean(fundings_per_10k, na.rm = TRUE),
    .groups = "drop"
  )

# Bar chart: average fundings_per_10k by month
bar_monthly <- ggplotly(
  ggplot(monthly_data, aes(x = month, y = fundings_per_10k, fill = campaign_name)) +
    geom_col(position = position_dodge(width = 5), width = 20, color = "gray20", alpha = 0.85) +
    scale_fill_manual(values = campaign_colors) +
    labs(title = "Monthly Fundings per 10k Total Mail sent by Campaign", x = "Month", y = "Fundings per 10k", fill = "Campaign") +
    theme_minimal(base_size = 10) +
    theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1))
) %>% layout(title = list(text = "Monthly Fundings per 10k by Campaign"))

# Box plot: distribution of fundings_per_10k by campaign
box_monthly <- ggplotly(
  ggplot(plot_data_datecutoff, aes(x = campaign_name, y = fundings_per_10k, fill = campaign_name)) +
    geom_boxplot(alpha = 0.7, color = "gray20") +
    scale_fill_manual(values = campaign_colors) +
    labs(title = "Distribution of Fundings per 10k by Campaign", x = "Campaign", y = "Fundings per 10k") +
    theme_minimal(base_size = 10) +
    theme(legend.position = "none", axis.text.x = element_text(size = 8))
) %>% layout(title = list(text = "Distribution of Fundings per 10k by Campaign"))
```


### Monthly performance of number of funded loans per 10,000 total mail

We explore further to see if any patterns emerge when looking at efficiency by month or within the summer time frame.

The monthly funding bar chart seen below that approximates the number of fundings one would get per 10,000 total mail sent out, we are seeing that as time goes on, Camber may in fact outperform Amsive though that remains to be seen in time.


```{r}
bar_monthly
```
### Summer mail data analysis

Furthermore, we narrow down our data to between 04/03/2025 - 08-01-2025. This is done because enough time has gone by to where our ad campaigns have had enough exposure.

We see that based on amount of mail sent out, that Camber looks to have better leads as more loans are funded per 10,000 mail sent. This may be worth looking into more.

```{r}
p <- ggplot(plot_data_datecutoff %>% filter( mail_date <= as.Date("2025-08-01")), aes(x = mail_date , y = total_mail_pieces, fill = campaign_name)) +
  geom_col(position = position_dodge(width = 0.01), width = 2, color = "gray20", alpha = 0.85) +
scale_fill_manual(values = c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA" ,
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)) +
  labs(
    title = "游늵 Total Mail Pieces by date sent out (05/05/2025 - 08-01-2025)",
    x = "Mail Date",
    y = "Total Mail by date",
    fill = "Campaign"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplotly(p)
```


```{r}
p <- ggplot(plot_data_datecutoff %>% filter( mail_date <= as.Date("2025-08-01")), aes(x = total_mail_pieces, y = fundings_per_10k, fill = campaign_name)) +
  geom_col(position = position_dodge(width = 0.01), width = 200, color = "gray20", alpha = 0.85) +
scale_fill_manual(values = c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA" ,
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)) +
  labs(
    title = "游늵 Fundings vs Total Mail Pieces sent out (05/05/2025 - 08-01-2025)",
    x = "Mail Date",
    y = "Total Funded per 10k",
    fill = "Campaign"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplotly(p)
```


```{r}
p <- ggplot(plot_data_datecutoff %>% filter( mail_date <= as.Date("2025-08-01")), aes(x = campaign_name, y = fundings_per_10k, fill = campaign_name)) +
  scale_fill_manual(values = c(
  "Camber" = "#E26E5F",   
  "Amsive" = "#44CDDA" ,
  "Monster" = "#87d087",
  "Redstone" = "#AD2E1D",
  "Other" = "#979d5d"
)) +
  geom_boxplot(alpha = 0.7, color = "gray20") +
  labs(title = "游늵 Total Mail-To-Fund by Campaign (05/05/2025 - 08-01-2025)",
    x = "Mail Date",
    y = "Total Mail-To-Fund (%)",,
       fill = "Campaign") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")

ggplotly(p)
```



# Conclusion

So far, here are the observations that we see. 

When comparing Camber to Amsive which are our two dominant campaign ad agencies, we notice Camber out-performs Amsive when it comes to the number of calls we get per total mail sent, however under performs when it comes to conversion to locks and funds. 

When by-passing all of the metrics and directly looking at Total mail sent conversion to Funded loans, we see that Amsive does only slightly better 

**Important** We should probably be observing performance with respect to time, older ad campaigns have more funded loans. So we will need to review after some time has passed to see which loans will fund from our newer campaigns. 

# Further questions

1) What do we know about Camber and Amsive? Or other ad agencies? Is there anything we know that one does over the other that can help us?

2) Will these types of reports be better weekly or monthly? At least for measuring one agency against another. We can create other reports weekly for # calls, calls per loan officer etc...

3) Why is early summer performance better than later summer performance? Is this an industry pattern? Are there economic factors that could be at play?

# Future considerations.
- 游늳 Campaign ROI (Add in the cost of each type of ad)
- Look at loan amount distribution
- How much can we play around with ad metrics (which locations mail is sent to, time of day etc...)
- 游 Lead quality score 
- Monster total mail count needs to be populated
- Total volume of calls, locks, funds
- When we get more data, it might be wise to match against industry predictions of rates to know when to deploy more or less marketing.

# Fix Me 

We have some mailing campaign dates unaccounted for that could help us in future analyses. Can we get an update on them?

```{r}
# NA values Need to either ignore these or populate the total mail pieces(Lower case and no spaces for snake type)
maildata_totalmail_na <- maildata %>% filter(is.na(total_mail_pieces))


# 游릴 Render searchable table with column filters
datatable(
  maildata_totalmail_na,
  filter = "top",
  editable = TRUE,
  options = list(
    pageLength = 5,
    scrollX = TRUE,
    dom = 'Bfrtip',  # 游녣 enables buttons
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')  # 游녣 export formats
  ),
  extensions = 'Buttons',
  rownames = FALSE,
  caption = "游늶 Total Mail Data missing from select dates"
)
```

--End--